Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by the Galaxy Cluster Abell 2744

### 2015-05-20 snTomas.tex
modified source plane min. and specz frac discussion

\change{  There are several strategies for mitigating this well known bias.
Optimizing a model in the image plane can  avoid this bias entirely \citep{Broadhurst:2005,Zitrin:2009a}. Alternatively, one may guard against it by using
a modified source plane minimization that is constrained not to
generate overly small re-lensed sources \citep{Sendra:2014,Diego:2014}.
Finally, the effect of this bias should be reduced when one uses many strong
lensing constraints over a wide range of redshifts. }

\change{ Of the 17 models examined here, both of the Zitrin models 
follow the first strategy, using image-plane optimization.  The
Zitrin-LTM model delivers a significantly discrepant magnification,
while the Zitrin-NFW latter is within 1$\sigma$ of the SN
magnification.  The Diego model uses the second strategy of restricted
source-plane minimization, and reports a magnification very close to
the measured value.  The CATS(v2) model is the most extreme example of
the final strategy, as it incorporates more multiply-imaged sources
over a wider redshift range than any other model. However, this model
is also the most discrepant, with a predicted $\mu$ that is $>4\sigma$
from the SN magnification.  Thus, the results from this simplistic
model comparison are mixed.  We therefore cannot conclude that source
plane minimization alone is the root cause of the observed systematic
bias. }

@@

\change{
In the right panel of Figure~\ref{fig:Nspecz} we examine an
alternative explanation by plotting the model tension against the
fraction of strong-lensing constraints that have a spectroscopic
redshift. Here we see that all three of the testable model series
(Bradac,Lam,CATSv2) become {\it more} accurate as the spec-z fraction
increases.\footnote{Of course this apparent correlation does not imply
any direct causation. Consider the limit of just a single
multiply-imaged galaxy constraint: the spec-$z$ fraction could be 1.0
but the model would be wildly unconstrained.}  The spec-$z$ fraction
here serves as a crude stand-in for measuring how
stringently the strong-lensing constraints are selected in these
models.  
}

\change{
The SN \tomas\ comparison therefore supports the notion that the {\it
quality} of strong-lensing constraints is just as important as the
{\it quantity}} \changeR{ -- at least for computing magnifications of sources outside the strong-lensing region. Once a sufficient number of robust multiply-imaged systems have been included (perhaps $\sim$10) most models will be dominated by systematic uncertainties such as those described in Section~\ref{sec:LensModelErrors}.  To improve the accuracy of magnification predictions with a large number of strong-lensing constraints, one } 
\change{
should employ a strict vetting of the multiply-imaged systems.  Each
system used should ideally have a spectroscopic redshift, or at least
a very well constrained photometric redshift.  The primary value in
this strict vetting is to avoid erroneous redshifts being assigned to
multiply-imaged systems that are unconstrained in redshift space.
Such redshift errors are especially problematic for relatively low-$z$
background systems: at lower redshifts the model-derived deflection
angle and magnification show a more rapid variation with the redshift
of the background galaxy than for similarly positioned high redshift
galaxies.}

>>>>

\change{  There are several strategies for mitigating this well known bias.
Optimizing a model in the image plane can avoid this bias
entirely \citep{Broadhurst:2005,Zitrin:2009a}.} \changeR{The
Sharon(v2), Zitrin-LTM, Zitrin-NFW, and CATS(v2-2.2) models all use
image plane minimization.}  \change{Alternatively, one may guard against this
bias by using a modified source plane minimization that is constrained
not to generate overly small re-lensed
sources \citep{Sendra:2014,Diego:2014}.} \changeR{In our test set, this
second strategy is employed by the Diego model.}  \change{Finally, the
effect of this bias should be reduced when one uses many strong
lensing constraints over a wide range of redshifts.} \changeR{The
CATS(v2) and CATS(v2.1) models have the largest number of
strong-lensing constraints, using 50 and 55 multiply-imaged systems,
respectively.}

\changeR{ Although many of the tested models utilize these 
strategies to avoid a source plane minimization bias,
Table~\ref{tab:PredictedMagnifications} and
Figure~\ref{fig:LensingTest} show that these models do not uniformly
deliver more accurate magnification predictions.  The most direct test
of this is in the Sharon and CATS model series.  In both cases the v1
model used the faster source plane minimization approach, but the v2
model was constructed with the more costly image plane minimization.
Neither of those models show a significant improvement in model
accuracy from v1 to v2.  T his provides a strong indication that the
observed tension between models and the SN observation cannot be
entirely attributed to a bias arising from source plane minimization.}

@@

\change{
In the right panel of Figure~\ref{fig:Nspecz} we examine an
alternative explanation by plotting the model tension against the
fraction of strong-lensing constraints that have a spectroscopic
redshift. 
For the SN \tomas\ magnification prediction, we see that all three of
the testable model series (Bradac,Lam,CATSv2) become {\it more}
accurate as the spec-z fraction increases.\footnote{Of course this
apparent correlation does not imply any direct causation. Consider the
limit of just a single multiply-imaged galaxy constraint: the spec-$z$
fraction could be 1.0 but the model would be wildly unconstrained.}
The spec-$z$ fraction here serves as a crude stand-in for measuring
how stringently the strong-lensing constraints are selected in these
models.  }

\change{
The SN \tomas\ comparison therefore supports the notion that the {\it
quality} of strong-lensing constraints is just as important as the
{\it quantity}} \changeR{ -- at least for computing magnifications of sources outside the strong-lensing region. Once a sufficient number of robust multiply-imaged systems have been included (perhaps $\sim$10) most models will be dominated by systematic uncertainties such as those described in Section~\ref{sec:LensModelErrors}.  To improve the accuracy of magnification predictions with a large number of strong-lensing constraints, one } 
\change{
should employ a strict vetting of the multiply-imaged systems.  Each
system used should ideally have a spectroscopic redshift, or at least
a very well constrained photometric redshift.  The primary value in
this strict vetting is to avoid erroneous redshifts being assigned to
multiply-imaged systems that are unconstrained in redshift space.
Such redshift errors are especially problematic for relatively low-$z$
background systems: at lower redshifts the model-derived deflection
angle and magnification show a more rapid variation with the redshift
of the background galaxy than for similarly positioned high redshift
galaxies.}  \changeR{This conclusion should be unsurprising, as for
example, \citet{Bayliss:2015} have shown that cosmological
uncertainties are smaller for models that use a large fraction of
strong-lensing constraints with spectroscopic redshifts,
and \citet{Johnson:2014} have shown a case study where adding
spectroscopic redshift information changes the inferred magnification
by $\sim$10\%.}
